Air cargo load and route planning in pickup and delivery operations

### 2023-07-20 CAIE/CIE.tex
mpShims tests on CIE.tex
May be discarded

@@

Wong and Ling \cite{wong2020}A developed a mathematical model and a tool based on mixed integer programming for optimizing cargo in aircraft with different pallet configurations. Balance constraints and the presence of dangerous items were considered. Wong {\it et al.} \cite{eugene2021} integrated this tool to a digital simulation model, with a visualization and validation system, based on sensors that alert about load deviations.

@@

@@

@@

This research was partially supported by \textit{São Paulo Research Foundation} (FAPESP, grant 2016/01860-1).

@@

\bibitem{LopezIbanezManuel2016} M. López-Ibáñez, J. Dubois-Lacoste, L.P. Cáceres, M. Birattari and T. Stützle, The irace package: Iterated racing for automatic algorithm configuration, {\it Operations Research Perspectives}, Vol. 3, pp. 43-58, 2016.

>>>>

 \setlength{\fboxsep}{0.005pt}
\newcommand{\tmpframe}[1]{\fbox{#1}}

@@

Wong and Ling \cite{wong2020}A?developed a mathematical model and a tool based on mixed integer programming for optimizing cargo in aircraft with different pallet configurations. Balance constraints and the presence of dangerous items were considered. Wong {\it et al.} \cite{eugene2021} integrated this tool to a digital simulation model, with a visualization and validation system, based on sensors that alert about load deviations.

@@

		\multirow{2}{*}{\it mpShims} & \multirow{2}{*}{240*}  & $f$ & 8.32 & 12.14 & 13.19 & 14.60   & 13.52  & 11.57 & 16.86 & 18.21 & 20.52   & 18.06  & 17.58 & 25.21 & 26.46 & 29.11   & 26.14 \\ % 
&         & {\bf time (s)}                                          & 1    & 2     & 5     & 13      & 71     & 1     & 2     & 6     & 15      & 79     & 2     & 2     & 8     & 21      & 102   \\ %

@@

\begin{figure}[H]
	\centering
	\tmpframe{\includegraphics[scale=0.5]{Images/mpShimsResouces.png}}
	\captionof{figure}{{\it mpShims} resources consumption}
	\label{fig:mpShimsResouces}
\end{figure}

@@

This research was partially supported by \textit{S?o Paulo Research Foundation} (FAPESP, grant 2016/01860-1).

@@

\bibitem{LopezIbanezManuel2016} M. L?pez-Ib??ez, J. Dubois-Lacoste, L.P. C?ceres, M. Birattari and T. St?tzle, The irace package: Iterated racing for automatic algorithm configuration, {\it Operations Research Perspectives}, Vol. 3, pp. 43-58, 2016.
